Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
Add important points we want to say in intro
Whitespace change

In BDD, all behavior should be documented, together with some
\emph{evidence} for that behavior.
For this purpose,
we brought a test method from other programming language community and
extended missing features.
In particular, we introduced Doctest~\cite{doctest} and
integrated it with QuickCheck~\cite{quickcheck}
for user documentation.
For code documentation,
we make use of Hspec inspired by RSpec~\cite{rspec}
and we proposed some combinators to set expectations
about \emph{code example}\/s.

@@

@@

\begin{quote}
\emph{kazu: How implemneted the ``property'' function? Trystan or Simon?}
\end{quote}

>>>>

In BDD, all behavior should be documented, together with some
\emph{evidence} for that behavior.

For this purpose, we brought a test method from other programming
language community and extended missing features.  In particular, we
introduced Doctest~\cite{doctest} and integrated it with
QuickCheck~\cite{quickcheck} for user documentation.

For code documentation, we make use of Hspec inspired by
RSpec~\cite{rspec} and we proposed some combinators to set
expectations about \emph{code example}\/s.

@@

\begin{quote}\begin{itemize}
    \item
        We want to use properties and examples to provide evidence for
        behavior.
    \item
        Haddock already has markup support for interactive examples,
        and Doctest can verify them.
    \item
        It is not possible to use properties in Haddock comments and
        automatically test them.
\end{itemize}\end{quote}

@@
